### 2018-07-09 latex/results.tex
Fixed some things in results

As shown in Figure~\ref{fig:phylo_distribution}A, bacteria, fungi, and plants predominantly possess NADA and only a few of them harbour NamPRT. In contrast, Metazoa predominantly lost NADA amd have NamPRT together with NNMT. NNMT seems to have arisen \textit{de~novo} in the most recent common ancestor of Ecdysozoa and Lophotrochozoa (fig.~\ref{fig:phylo_distribution}B). As we were unable to find any \textit{NNMT} gene with an e-value below xxx \todo{Mathias B. include e-value} in fungi or plants. The gene with the highest sequence similarity in \textit{S.~cerevisiae} is ... with proven function ... \todo{Mathias B: include values}.

@@

So far we have not discussed the effect of NADA on Nam-salvage and especially the question, why it is lost in vertebrates. As selection during evolution results usually from competition for resources, we built a two compartment model, based on the pathway model described above. One compartment contains NADA, while the other one contains either NamPRT alone, or together with NNMT. Both compartments share a limited  Nam source (for details, see experimental procedures and suppl. tab.~S2). Without NNMT, the compartment containing NADA shows slightly lower NAD consumption rates (fig.~\ref{fig:NNMT_comp_advantage}A), but is able to maintain much higher NAD concentrations especially at low cell division rates (fig.~\ref{fig:NNMT_comp_advantage}B). At high cell division rates, steady state concentrations in both compartments are similar. This might explain why in bacteria, that often have relatively high growth rates, both systems can co-exist.

In the presence of NNMT, the NamPRT compartment has both higher NAD consumption rates and higher steady state NAD concentrations than the compartment containing NADA (fig.~\ref{fig:NNMT_comp_advantage}C and~D). The higher NAD concentrations in the compartment containing NamPRT and NNMT can, however, only be maintained  if the affinity of NamPRT for Nam is high enough, corresponding to a low $K_{M}$. If the affinity of NamPRT is too low (high $K_{M}$), the NADA compartment is able to maintain higher NAD concentrations, but it still has a lower the NAD consumption flux.  Taken together, the results suggest that the NADA pathway might have become obsolete upon emergence of the  high affinity NamPRT This in turn might have been induced by the appearance of NNMT.

>>>>

As shown in Figure~\ref{fig:phylo_distribution}A, bacteria, fungi, and plants predominantly possess NADA and only a few of them harbour NamPRT. In contrast, Metazoa predominantly lost NADA amd have NamPRT together with NNMT. NNMT seems to have arisen \textit{de~novo} in the most recent common ancestor of Ecdysozoa and Lophotrochozoa (fig.~\ref{fig:phylo_distribution}B). As we were unable to find any \textit{NNMT} gene with an e-value below 0.1 in fungi or plants. The gene with the highest sequence similarity in \textit{S.~cerevisiae} is ... with proven function ... \todo{Mathias B: include values} \todo{Answer from MB: There was not a single hit outside Metazoa}.

@@

So far, we did not discuss the effect of NADA on Nam salvage and especially the question, why it is lost in vertebrates. As selection during evolution results usually from competition for resources, we built a two compartment model, based on the pathway model described above. One compartment contains NADA, while the other one contains either NamPRT alone or together with NNMT. Both compartments share a limited Nam source (for details, see experimental procedures and suppl. tab.~S2). Without NNMT, the compartment containing NADA shows slightly lower NAD consumption rates (fig.~\ref{fig:NNMT_comp_advantage}A), but is able to maintain much higher NAD concentrations especially at low cell division rates (fig.~\ref{fig:NNMT_comp_advantage}B). At high cell division rates, steady state concentrations in both compartments are similar. This might explain why in bacteria, that often have relatively high growth rates, both systems can co-exist.

In the presence of NNMT, the NamPRT compartment has both higher NAD consumption rates and higher steady state NAD concentrations than the compartment containing NADA (fig.~\ref{fig:NNMT_comp_advantage}C and~D). The higher NAD concentrations in the compartment containing NamPRT and NNMT can, however, only be maintained if the affinity of NamPRT for Nam is high enough. If the substrate affinity of NamPRT is too low (high $K_{M}$), the NADA compartment is able to maintain higher NAD concentrations, but still has a lower NAD consumption flux. Taken together, the results suggest that the NADA pathway might have become obsolete upon emergence of the high affinity NamPRT. This in turn might have been induced by the appearance of NNMT.
